---
title: "SML ASSIGNMENT 1"
author: "Détagnon Bernic GBAGUIDI"
date: "2024-01-12"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(pROC)
library(caret)
library(boot)
library(MASS)
library(randomForest)
library(class)
library(rpart)
library(dslabs) 
library(corrplot)
```

## Exercice 1

```{r}
mnist <- read_mnist() # Read in the MNIST data
```


```{r}

### loading train set
xtrain <- mnist$train$images
ytrain <- mnist$train$labels
ytrain <- as.factor(ytrain)

### loading test set

xtest <- mnist$test$images
ytest <- mnist$test$labels
ytest <- as.factor(ytest)

#### loading only 1 and 7 from train set

xtrain17 <- xtrain[ytrain==1 | ytrain==7,]
ytrain17 <- ytrain[ytrain==1 | ytrain==7]
ytrain17 <- as.factor(as.numeric(as.vector(ytrain17)))

#### loading only 1 and 7 from test set

xtest17 <- xtest[ytest==1|ytest==7,]
ytest17 <- ytest[ytest==1|ytest==7]
ytest17 <-  as.factor(as.numeric(as.vector(ytest17)))
```



### Question 1 Let extract a fragment of the large data set

In order to have a good representation of the level '1' and '7' and because we are going to do a classification , stratifed sampling is a good approach.
This function below come from the Rmarkdown file of the lecturer Enerst FOKOUE.

It allow to do a stratified sampling and also respect de proportion for train set and test set according to the way it is in the MNIST data set.

The proportion test/train =0.167.

According to percentage of representation of each level we can deduce the n and m.

Percentage of level=0.4

n=5203
m=865
```{r}
stratified.holdout <- function(y, ptr)
   {
     n              <- length(y)
     labels         <- unique(y)       # Obtain classifiers
     id.tr          <- id.te <- NULL
     # Loop once for each unique label value
  
     y <- sample(sample(sample(y)))
  
     for(j in 1:length(labels)) 
     {
        sj    <- which(y==labels[j])  # Grab all rows of label type j  
        nj    <- length(sj)           # Count of label j rows to calc proportion below
        
        id.tr <- c(id.tr, (sample(sample(sample(sj))))[1:round(nj*ptr)])
      }                               # Concatenates each label type together 1 by 1
  
      id.te  <- (1:n) [-id.tr]          # Obtain and Shuffle test indices to randomize                                
  
      return(list(idx1=id.tr,idx2=id.te)) 
   }  




hold  <- stratified.holdout(ytrain17, 0.4) 
   id.tr <- hold$idx1
   ntr   <- length(id.tr)
   
   p   <- ncol(xtrain)

   

   hold  <- stratified.holdout(ytest17, 0.4)
   id.te <- hold$idx1
   nte   <- length(id.te)
   
  
   xtr <- xtrain17[id.tr,]
   ytr17 <- ytrain17[id.tr]
   xte <- xtest17[id.te,]
   yte17 <- ytest17[id.te]

```


In the MNIST dataset we have the number of input that is 784 . In order to make our machine faster we will accept to lose a bit in accuracy using the reputated tool PCA. It consist of reducing the number of variable based on the fact that some of them are correlated.


```{r}
  
    pca.tr17 <- prcomp(xtr)

   pv <- cumsum((summary(pca.tr17)$sdev)^2)
   
  
   lambda <- (summary(pca.tr17)$sdev)^2
   pv <- cumsum(lambda/sum(lambda))
  
   
   q <- min(which(pv>0.90))
   
   q    
      
   xtr17 <- predict(pca.tr17,xtr)[,1:q]
   xte17 <- predict(pca.tr17,xte)[,1:q]
```




### Question 2  Let find the confusion matrice for each data set and for each machine.

####For the first machine 1NN
```{r}
##### 1NN

ytr.1nn <- knn(xtr17, xtr17, ytr17, k=1)

   conf.mat.tr.1nn <- table(ytr17, ytr.1nn)
   
   #conf.mat.tr.1nn
   
yte.1nn <- knn(xtr17, xte17, ytr17, k=1)

   conf.mat.te.1nn <- table(yte17, yte.1nn)
   
   #conf.mat.te.1nn   
   print(conf.mat.tr.1nn)
   print(conf.mat.te.1nn)
```


#### For the second machine 9NN
```{r}
#### 9NN
ytr.9nn <- knn(xtr17, xtr17, ytr17, k=9)

   conf.mat.tr.9nn <- table(ytr17, ytr.9nn)
   
   #conf.mat.tr.1nn
   
yte.9nn <- knn(xtr17, xte17, ytr17, k=9)

   conf.mat.te.9nn <- table(yte17, yte.9nn)
   
   #conf.mat.te.1nn   
   print(conf.mat.tr.9nn)
   print(conf.mat.te.9nn)

```





#### For the third machine 18NN

```{r}
ytr.18nn <- knn(xtr17, xtr17, ytr17, k=18)

   conf.mat.tr.18nn <- table(ytr17, ytr.18nn)
   
   #conf.mat.tr.1nn
   
yte.18nn <- knn(xtr17, xte17, ytr17, k=18)

   conf.mat.te.18nn <- table(yte17, yte.18nn)
   
   #conf.mat.te.1nn   
   print(conf.mat.tr.18nn)
   print(conf.mat.te.18nn)
```



#### For the fourth machine 27NN
```{r}
### 27NN


ytr.27nn <- knn(xtr17, xtr17, ytr17, k=27)

   conf.mat.tr.27nn <- table(ytr17, ytr.27nn)
   
   #conf.mat.tr.1nn
   
yte.27nn <- knn(xtr17, xte17, ytr17, k=27)

   conf.mat.te.27nn <- table(yte17, yte.27nn)
   
   #conf.mat.te.1nn   
   print(conf.mat.tr.27nn)
   print(conf.mat.te.27nn)

```



### Question 3  Let display the ROC curves for each data set applying for KNN

#### For the train set
```{r}


roc.tr1nn <- roc(ytr17,as.numeric(as.vector(ytr.1nn)))
roc.tr9nn <- roc(ytr17,as.numeric(as.vector(ytr.9nn)))
roc.tr18nn <- roc(ytr17,as.numeric(as.vector(ytr.18nn)))
roc.tr27nn <- roc(ytr17,as.numeric(as.vector(ytr.27nn)))
plot(roc.tr1nn,main="ROC Curves for the train set",
     col = "red", lty = 2, xlim = c(0, 1), ylim = c(0, 1))
lines(roc.tr9nn, col = "blue", lty = 2)
lines(roc.tr18nn, col = "green", lty = 2)
lines(roc.tr27nn, col = "purple", lty = 2)
legend("bottomright", legend = c("1NN", "9NN", "18NN", "27NN"),
       col = c("red", "blue", "green", "purple"), lty = 2)

```

#### For the test set
```{r}


roc.te1nn <- roc(yte17,as.numeric(as.vector(yte.1nn)))
roc.te9nn <- roc(yte17,as.numeric(as.vector(yte.9nn)))
roc.te18nn <- roc(yte17,as.numeric(as.vector(yte.18nn)))
roc.te27nn <- roc(yte17,as.numeric(as.vector(yte.27nn)))
plot.roc(roc.te1nn,main="ROC Curves for the test set",
         col = "red", lty = 2, xlim = c(0, 1), ylim = c(0, 1))
lines.roc(roc.te9nn, col = "blue", lty = 2)
lines.roc(roc.te18nn, col = "green", lty = 2)
lines.roc(roc.te27nn, col = "purple", lty = 2)
legend("bottomright", legend = c("1NN", "9NN", "18NN", "27NN"),
       col = c("red", "blue", "green", "purple"), lty = 2)

```

### Question 4 Let find a False Positive and False Negative.

### N B:
For my machines , all of them don't have a False Negative
          
and normally this is good and explain that the machine 
          
perform well. This lead in fact that for the plotting 
i won't have False negative displayed. Intead it will be a blank window.

#####For 1NN

```{r}

#par(mfrow=c(4,2))
falseNegative <- which(yte17==1&yte.1nn==7)
falsePositive <- which(yte17==7&yte.1nn==1)

#### 1 wrong predicted
image(1:28, 1:28, matrix(xte[falseNegative[1],], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True image")
    image(1:28, 1:28, matrix(xte[2,], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Negative")

image(1:28, 1:28, matrix(xte[falseNegative[2],], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True image")
    image(1:28, 1:28, matrix(xte[2,], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Negative")

##### 7 wrong predicted      
image(1:28, 1:28, matrix(xte[falsePositive[1],], nrow=28)[ , 28:1], 
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True Image")
    image(1:28, 1:28, matrix(xte[1,], nrow=28)[ , 28:1], 
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Positive")
image(1:28, 1:28, matrix(xte[falsePositive[2],], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True image")
    image(1:28, 1:28, matrix(xte[1,], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Positive")

```


#### For 9NN

```{r}
falseNegative <- which(yte17==1&yte.9nn==7)
falsePositive <- which(yte17==7&yte.9nn==1)

#### 1 wrong predicted
image(1:28, 1:28, matrix(xte[falseNegative[1],], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True image")
    image(1:28, 1:28, matrix(xte[2,], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Negative")

image(1:28, 1:28, matrix(xte[falseNegative[2],], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True image")
    image(1:28, 1:28, matrix(xte[2,], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Negative")

##### 7 wrong predicted      
image(1:28, 1:28, matrix(xte[falsePositive[1],], nrow=28)[ , 28:1], 
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True Image")
    image(1:28, 1:28, matrix(xte[1,], nrow=28)[ , 28:1], 
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Positive")
image(1:28, 1:28, matrix(xte[falsePositive[2],], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True image")
    image(1:28, 1:28, matrix(xte[1,], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Positive")

```
#### For 18NN

```{r}
falseNegative <- which(yte17==1&yte.18nn==7)
falsePositive <- which(yte17==7&yte.18nn==1)

#### 1 wrong predicted
image(1:28, 1:28, matrix(xte[falseNegative[1],], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True image")
    image(1:28, 1:28, matrix(xte[2,], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Negative")

image(1:28, 1:28, matrix(xte[falseNegative[2],], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True image")
    image(1:28, 1:28, matrix(xte[2,], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Negative")

##### 7 wrong predicted      
image(1:28, 1:28, matrix(xte[falsePositive[1],], nrow=28)[ , 28:1], 
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True Image")
    image(1:28, 1:28, matrix(xte[1,], nrow=28)[ , 28:1], 
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Positive")
image(1:28, 1:28, matrix(xte[falsePositive[2],], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True image")
    image(1:28, 1:28, matrix(xte[1,], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Positive")

```


#### For 27NN
```{r}
falseNegative <- which(yte17==1&yte.27nn==7)
falsePositive <- which(yte17==7&yte.27nn==1)

#### 1 wrong predicted
image(1:28, 1:28, matrix(xte[falseNegative[1],], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True image")
    image(1:28, 1:28, matrix(xte[2,], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Negative")

image(1:28, 1:28, matrix(xte[falseNegative[2],], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True image")
    image(1:28, 1:28, matrix(xte[2,], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Negative")

##### 7 wrong predicted      
image(1:28, 1:28, matrix(xte[falsePositive[1],], nrow=28)[ , 28:1], 
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True Image")
    image(1:28, 1:28, matrix(xte[1,], nrow=28)[ , 28:1], 
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Positive")
image(1:28, 1:28, matrix(xte[falsePositive[2],], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="")
     title(main = "True image")
    image(1:28, 1:28, matrix(xte[1,], nrow=28)[ , 28:1],
     col = gray(seq(0, 1, 0.05)), xlab = "", ylab="",)
    title(main = "False Positive")

```


### Question 5  COMMENT



We can noticed that for each machine the false positives and false negatives  seem to be the same.
If we can go back to the matrices of confusion , i'm expecting the rate of error decrease when the K is increasing but that's not realy the case . There are not a real partern to deduce. Making an extra reseach in google , the best K can be deduced by doing a cross validation.
Let remark also that my machines made a lot of errors on the train data what is surprising.


## Exercice 2

1- Let find and write $E(Y|X)$.

We have \[
p_1(y|x) = \frac{1}{{\sqrt{(2\pi\frac{9}{(\pi^2)})}}} \exp\left(-\frac{\pi^2}{18} \left(y - \frac{\pi}{2}x - \frac{3\pi}{4}\cos\left(\frac{\pi}{2}(1 + x)\right)\right)^2\right)
\]
It is  a gaussian distribution with parameter \[\mu=\frac{\pi}{2}x +\frac{3\pi}{4}\cos\left(\frac{\pi}{2}(1 + x)\right)\] and \[ \sigma^2= \frac{9}{\pi^2}\]

Then we can conclude that \[  E(Y|X) =\frac{\pi}{2}x +\frac{3\pi}{4}\cos\left(\frac{\pi}{2}(1 + x)\right)\]


2- Generate  a join distribution sampling.
```{r}
set.seed(19671210)
n=99
X <- runif(n ,min = 0,max = 2*pi)
mu=(pi/2)*X+(0.75*pi*cos((pi/2)*(1+X)))
sigma=3/pi
Y=rnorm(n,mu,sigma)
```

3- Display the scarter plot
```{r}
#scatterplot(X,Y)
data <- data.frame(X,Y)
ggplot(data,aes(X,Y))+
  geom_point()
```

4-
  1) Let find \[ f^*(X) = \arg\min_f R(f) = \arg\min_f E[l(Y, f(X))]
  \]
  
  We have 
  
  
  \begin{align*}
  R(f)=&E(l(Y,f(X))) \\
      =&\int \int (y-f(x))^2P_{X,Y}(x,y)dxdy  \\
      =&\int \int  (y-f(x))^2P_X(x)P_{Y|X}(y|x)dxdy  \mbox{  $\quad$  ( Bayes)  }  \\
      =& \int P_X(x)\left(\int (y-f(x))^2P_{Y|X}(y|x) dy \right)dx  \\
      =&\int P_X(x) E((Y-f(x))^2|X=x)dx
  \end{align*}
  
  
  
  With the expression obtained, we can deduce that the $f$ that minimize $R(f)$  is the same that minimize $P_X(x) E((Y-f(x))^2|X=x)$ with $x$ fixed. 
  
  Now let denote $Q(f(x))=P_X(x) E((Y-f(x))^2|X=x)$
  
  
   \begin{align*}
  Q(f(x))=&P_X(x) E((Y-f(x))^2|X=x)  \\
        =& P_X(x) \left(E((Y^2-2f(x)Y+f(x)^2)|X=x) \right)   \\
        =& P_X(x) \left(E(Y^2|X=x)-2f(x)E(Y|X=x)+f(x)^2) \right)   
    \end{align*}
  
  
   Let differenciate $Q(f(x))$ with respect to $f(x)$.
   
   
  We have $Q'(f(x))=P_X(x)(-2E(Y|X=x)+2f(x))$.
  
  When we equate to zero we will have $f(x)=E(Y|X=x)$.
  
  
  We can deduce that $f^{*}(x)=E(Y|X=x)$ because $Q''(f(x))=2 \ge 0$
  
  **Conclusion : $f^{*}(x)=E(Y|X=x)$**
  
  
  2) Let find \[
R^* = R(f^*) = \min_f R(f)
\]



  We have ,
  
  \begin{align*}
  R^* =& R(f^*) \\
  =& \int_{X \times Y} l(y, f(x))p_{XY}(x, y) \,dx \,dy \\
  =&\int_{X \times Y}(y-E(Y|X=x))^2P_{X,Y}(x,y)dxdy  \\
  =&\int_{X \times Y}(y-E(Y|X=x))^2\frac{1}{{2\pi\sqrt{(2\pi\frac{9}{(\pi^2)})}}} \exp\left(-\frac{\pi^2}{18} \left(y - \frac{\pi}{2}x - \frac{3\pi}{4}\cos\left(\frac{\pi}{2}(1 + x)\right)\right)^2\right)
dxdy  \\
=& \int_{X \times Y}(y-E(Y|X=x))^2\frac{1}{{2\pi\sqrt{(2\pi\frac{9}{(\pi^2)})}}} \exp\left(-\frac{\pi^2}{18} \left(y -E(Y|X=x) \right)^2\right)
dxdy  \\
  \end{align*}

  We can integrate in first time by integration by part  choosing 
  
  $u(x)=(y -E(Y|X=x))$ and
  
  $v'(x)=(y -E(Y|X=x)))\exp\left(-\frac{\pi^2}{18} (y -E(Y|X=x))^2 \right)$
  
  
  We will get the integral with respect to $dy$ that will be equal to $\frac{9}{\pi^2}\times \frac{1}{2\pi}$.
  
  
  Now we will integrate with respect to $dx$ on $[0;2\pi[$.
  
  We will get $$ R(f^*)=\frac{9}{\pi^2}$$
  
  
  
3)   Extrinsinc comparison between 4 machines for regression.
  
```{r}


set.seed(19671210)
replications <- 100

# vectors to store test errors
knn_errors <- numeric(replications)
linear_errors <- numeric(replications)
poly_errors <- numeric(replications)
tree_errors <- numeric(replications)

# Loop through replications
for (i in 1:replications) {
  
  # Split the data into training and test sets (60%-40%)
  idx <- createDataPartition(data$Y, p = 0.6, list = FALSE)
  train_data <- data[idx, ]
  test_data <- data[-idx, ]
  
  # Model training and prediction for kNN regression
 
  knn_model <- train(Y ~ X, train_data, method="knn")
  knn_errors[i] <- mean((test_data$Y - predict(knn_model, test_data))^2)
  
 
  
  # Model training and prediction for Linear regression
  linear_model <- lm(Y ~ X, data = train_data)
  linear_predictions <- predict(linear_model, newdata = test_data)
  linear_errors[i] <- mean((test_data$Y - linear_predictions)^2)
  
  # Model training and prediction for Polynomial regression (degree 2)
  poly_model <- lm(Y ~ poly(X, degree = 2), data = train_data)
  poly_predictions <- predict(poly_model, newdata = test_data)
  poly_errors[i] <- mean((test_data$Y - poly_predictions)^2)
  
  
  
  # Model training and prediction for Regression Tree Learner 
  tree_model <- rpart(Y ~ X, data = train_data, method = "anova")
  tree_predictions <- predict(tree_model, newdata = test_data)
  tree_errors[i] <- mean((test_data$Y - tree_predictions)^2)
}

## data set of error
error_data <- data.frame(
  kNN = knn_errors,
  Linear = linear_errors,
  Polynomial = poly_errors,
  Tree = tree_errors
)

# Plotting boxplots
boxplot(error_data, col = c("red", "blue", "green", "purple"),
        main = "Comparative Boxplots of Test Errors",
        ylab = "Test Error", 
        names = c("kNN", "Linear", "Polynomial", "Tree"))

```


```{r}
cat("We know that R*=9/pi^2 =0.91189 .
    \n The mean error test of each method is given by\n")
colMeans(error_data)
cat("We can see that all of them are greater that R* 
    but the 'knn'and the 'Tree' are the more close.
    \n The linear machine is the less better and 
    it is expected because looking at the scarter plot
    the relation between X and Y is not linear. ")
```




## Exercice 3 
```{r}
library(mlbench)
library(kernlab)


```

```{r}
data(DNA)  ### Binary predictor variables
data(BreastCancer)
data(spam) # Spam detection data set
leukemia<-read.csv('leukemia-data-1.csv') # DNA Microarray Gene Expression
prostate <- read.csv('prostate-cancer-1.csv') # DNA Microarray Gene Expression
colon <- read.csv('colon-cancer-1.csv')
```

```{r}
#### dataset DNA
## First intruction done in the second t=chunk of the exercice

### 

head(DNA,2)
cat("In the DNA dataset we have :",ncol(DNA),
    "colunm and ",nrow(DNA),"observations\n")
cat("The dimension of the output space is ",ncol(DNA)-1,
    "and the response is the variable class that
    is categorical with 3 level : ei,ie,neither(n)\n")
cat("From the dictionary (help(DNA))of the dataset
    it said that there are 180 indicator binary 
    variables that mean that the dataset
    is type-homogenous and scale-homogenous" )

cat("We have k=n/p=",nrow(DNA)/ncol(DNA)," . This is greater than 5 
    so this data set in term of size is not
    bad in context of hight dimensional setting")

set.seed(19671210)
par(mfrow=c(3,3))

set <- sample(1:(ncol(DNA)-1),9)
for (i in set){
 hist(as.numeric(as.vector(DNA[, i])), 
      main = paste("Variable", i), col = "yellow", border = "red")

  
}

cat("The dataset contain only categorical variable ,
    so that's not very useful to investigate about
    correlation and muticolinerarity")
```





```{r}

head(BreastCancer,1)
cat("In the BreastCancer dataset we have :",ncol(BreastCancer),"colunm and ",nrow(BreastCancer),"observations\n")
cat("The dimension of the output space is ",ncol(DNA)-2,
"and the response is the variable class that
is categorical with 2 level : 'benign' and 'malignant'\n")
cat("From the dictionary (help(BrestCancer))
of the dataset it said that the 9 predictor
have a value in range 0-10, 
that mean that the dataset is type-homogenous and scale-homogenous" )

cat("We have k=n/p=",nrow(BreastCancer)/ncol(BreastCancer)," . 
This is greater than 5 so this data set 
in term of size is not bad in context of hight dimensional setting")


par(mfrow=c(3,3))

#set <- sample(1:(ncol(BreastCancer)-1),9)
for (i in 2:10){
 hist(as.numeric(as.vector(BreastCancer[, i])),
      main = paste("Variable", i), col = "yellow", border = "red")

  
}


cat("The dataset contain only categorical variables ,
    so that's not very useful to investigate about
    correlation and muticolinerarity")

```






```{r}

head(spam,2)
cat("In the Spam dataset we have :",ncol(spam),
    "colunm and ",nrow(spam),"observations\n")
cat("The dimension of the output space is ",ncol(spam)-1,
    "and the response is the variable type that
    is categorical with 2 level : 'nonspam' and 'spam'\n\n")
cat("From the dictionary (help(Spam))of the dataset
    we can deduce that all the predictors are numeric 
    then it type-homogenous but in term of scale that's not
    the case because looking at the variable num415 
    it range is 0-5 whereas 
    for the variable capitalTotal it range is 1-15841  \n\n" )

cat("We have k=n/p=",nrow(spam)/ncol(spam)," .
    This is greater than 5 
    so this data set in term of size is not bad
    in context of hight dimensional setting")


par(mfrow=c(3,3))

set <- sample(1:(ncol(spam)-1),9)
for (i in set){
 hist(as.numeric(as.vector(spam[, i])),
      main = paste("Variable", i), col = "yellow", border = "red")

  
}
par(mfrow=c(1,1))
##### Correlation between some variables
corrplot(cor(spam[,sample(1:57,9)]))
cat("More is level more is the relation of corelation")
```


```{r}



head(leukemia,1)
cat("In the Leukemia dataset we have :",ncol(leukemia),
"colunm and ",nrow(leukemia),"observations\n\n")
cat("The dimension of the output space is ",ncol(leukemia)-1,
"and the response is
the variable Y that is categorical
with 2 level : '0' and '1'\n\n")
cat(" We do not have acces to the dictionnary 
of the the dataset leukemia.
So I made an exploration of the dataset .
I deduced that all the predictors are numeric 
so it's type homogenous. To know if it it is scale-homogenous
i reseached the mean of the each predictor(colMean(leukemia)),
then i inspected the distribution by ploting the boxplot and
of course i looked at the outliers and the max was 3.271207. 
I concluded with my finding that it is scale-homogenous.    \n\n" )

cat("We have k=n/p=",nrow(leukemia)/ncol(leukemia)," . 
    This is very less than 5 so this data set 
    in term of size is very bad in context 
    of hight dimensional setting")


par(mfrow=c(3,3))

set <- sample(2:(ncol(leukemia)),9)
for (i in set){
 hist(as.numeric(as.vector(leukemia[, i])),
      main = paste("Variable", i), col = "yellow", border = "red")
}

#### correlation of some variable
par(mfrow=c(1,1))
corrplot(cor(leukemia[,sample(2:ncol(leukemia),9)]))

cat("More is level more is the relation of corelation")
```




```{r}



head(prostate,1)
cat("In the Prostate dataset we have :",ncol(prostate),
"colunm and ",nrow(prostate),"observations\n\n ")
cat("The dimension of the output space is ",ncol(prostate)-1,
"and the response is the variable Y that 
is categorical with 2 level : '0' and '1'\n\n")
cat(" We do not have acces to the dictionnary
of the the dataset prostate. 
So I made an exploration of the dataset .
I deduced that all the predictors are numeric
so it's type homogenous. To know if it it is scale-homogenous
i reseached the mean of the each predictor(colMean(prostate)),
then i inspected the distribution by ploting the boxplot
and of course i looked at the outliers and the max was 7.5599. 
I concluded with my finding that it is scale-homogenous. \n\n" )

cat("We have k=n/p=",nrow(prostate)/ncol(prostate)," .
This is very less than 5 so this data set 
in term of size is very bad in context
of hight dimensional setting")


par(mfrow=c(3,3))

set <- sample(2:(ncol(prostate)),9)
for (i in set){
 hist(as.numeric(as.vector(prostate[, i])),
      main = paste("Variable", i), col = "yellow", border = "red")
}
par(mfrow=c(1,1))
corrplot(cor(prostate[,sample(2:ncol(prostate),9)]))

cat("More is level more is the relation of corelation")
```


```{r}


head(colon,1)
cat("In the Colon dataset we have :",ncol(colon),
"colunm and ",nrow(colon),"observations\n\n ")
cat("The dimension of the output space is ",ncol(colon)-1,
    "and the response is the variable colon.y
    that is categorical with 2 level : '1' and '2'\n\n")
cat(" We do not have acces to the dictionnary 
    of the the dataset Colon.
    So I made an exploration of the dataset .
    I deduced that all the predictors are numeric 
    so it's type homogenous.
    To know if  it is scale-homogenous i reseached the mean of
    the each predictor(colMean(colon)),
    then i inspected the distribution by ploting the boxplot 
    and of course i looked at the outliers and the max was 3.330481. 
    I concluded with my finding that it is scale-homogenous. \n\n" )

cat("We have k=n/p=",nrow(colon)/ncol(colon)," .
    This is very less than 5 so this data set 
    in term of size is very bad in context of hight dimensional setting")


par(mfrow=c(3,3))

set <- sample(2:(ncol(colon)),9)
for (i in set){
 hist(as.numeric(as.vector(colon[, i])),
      main = paste("Variable", i), col = "yellow", border = "red")
}

par(mfrow=c(1,1))
corrplot(cor(colon[,sample(2:ncol(colon),9)]))

cat("More is level more is the relation of corelation")
```










